Domain Specific Language for high performance computing

### 2024-02-09 paper/paper.tex
Lennard Jones data

\begin{lstlisting}[frame=single, caption=hoge]
//(1) include part
#include<math>
#include<immintrin.h>
int kernel( (2) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
  //(3) decleare tmp variable
  int i;
  int j;
  __m256d xi_tmp_v0;
  __m256d xi_tmp_v1;  
  __m256d xi_tmp_v2;
  __m256d eps2_tmp;
  // ... 
  // ... 
  // ... 
  //(4) def not class variables
  eps2_tmp = _mm256_set1_pd(eps2);
  // ... 
  // ... 
  // ...

  // (5) loop increment
  for(i = 0;i < n;i += 4) {
    // (6) Load EPI variable part
    int index_gather_0[4] = {0, 3, 6, 9};
    __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
    // ... 
    // ... 
    // ...

    // (7) initialize result temporary variable
    ai_tmp_v0 = _mm256_set1_pd(0.0);
    ai_tmp_v1 = _mm256_set1_pd(0.0);
    ai_tmp_v2 = _mm256_set1_pd(0.0);

    for(j = 0;j < n;j += 1) {
      // (8) Load EPJ variable part
         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
        // ... 
        // ... 
        // ...

      // (9) calculate interparticle
        dr_tmp_v0 = _mm256_sub_pd(xj_tmp_v0, xi_tmp_v0);
        dr_tmp_v1 = _mm256_sub_pd(xj_tmp_v1, xi_tmp_v1);
        dr_tmp_v2 = _mm256_sub_pd(xj_tmp_v2, xi_tmp_v2);
        ai_tmp_v0 += _mm256_div_pd(_mm256_mul_pd(//.....));
        ai_tmp_v1 += _mm256_div_pd(_mm256_mul_pd(//.....));
        ai_tmp_v2 += _mm256_div_pd(_mm256_mul_pd(//.....));

    }

    // (10) Store result part

  }
  return 0;
}
\end{lstlisting}

@@

>>>>

@@

\subsection{gravity interparticle}
ほぼ同じコードで実行

\begin{lstlisting}[frame=single, caption=Nbody-kernel.pyker, label=Nbody-kernel.pyker]
  EPI vec3<F64> ri
  EPJ vec3<F64> rj
  EPJ F64 mass
  EPJ F64 eps2
  FORCE vec3<F64> ai
  rij = ri - rj
  r2 = rij * rij + eps2
  r_inv = 1.0 / sqrt(r2)
  r2_inv = r_inv * r_inv
  mr_inv = mass * r_inv
  mr3_inv = r2_inv * mr_inv
  ai = mr3_inv * rij
  \end{lstlisting}

\begin{lstlisting}[frame=single, caption=Nbody-kernel.pikg, label=Nbody-kernel.pikg]
  EPI F64vec ri:r
  EPJ F64vec rj:r
  EPJ F64 mj:m

  EPJ F64 eps2:eps

  FORCE F64vec ai:acc

  rij = ri - rj
  r2 = rij * rij + eps2
  r_inv  = rsqrt(r2)
  r2_inv = r_inv * r_inv
  mr_inv  = mj * r_inv
  mr3_inv = r2_inv * mr_inv
  ai += mr3_inv * rij

non-simd

g++ -O3

\begin{tabular}{|l|r|r|} \hline
  N & Pyker & PIKG \\ \hline
  25000 & 6.725156 & 4.444766 \\
  10000 & 0.738918sec & 0.517324sec \\

 \\ \hline
\end{tabular}

\begin{lstlisting}[frame=single, caption=Nbody-kernel.pikg, label=Nbody-kernel.pikg]
  g++ -O3 -I ~/school/PIKG/PIKG/inc -mavx2 -mfma gravity_interparticle.cpp

  \begin{tabular}{|l|r|r|} \hline
    N & Pyker(sec) & PIKG(sec) \\ \hline
    50000 & 5.119071 & 3.333270\\
    25000 & 1.218129 & 1.148511 \\
    10000 & 0.143777 & 0.101594 \\
    1000 &  0.003521 & 0.002168 \\ \hline
  \end{tabular}

% \begin{tabular}{lrr}
%   N & pyker & PIKG \\
%   10000 & 0.143777sec & 0.101594sec \\
%   x & y & z 
%  \end{tabular}

\subsection{LennardJones}

\begin{lstlisting}[frame=single, caption=LennardJones-kernel.pyker, label=LennardJones-kernel.pyker]
EPI F64 rix
EPI F64 riy
EPI F64 riz
EPJ F64 rjx
EPJ F64 rjy
EPJ F64 rjz
EPJ F64 eps

FORCE F64 fx
FORCE F64 fy
FORCE F64 fz
FORCE F64 p
dx = rix - rjx
dy = riy - rjy
dz = riz - rjz
r2 = dx * dx + dy * dy + dz * dz + eps
r2i = 1.0 / r2
r6i = r2i * r2i * r2i
f = (48.0* r6i - 24.0) * r6i * r2i
fx = f * dx
fy = f * dy
fz = f * dz
p = 4.0 * (r6i) * (r6i - 1.0)
\end{lstlisting}
\begin{lstlisting}[frame=single, caption=LennardJones-kernel.pyker, label=LennardJones-kernel.pyker]
  EPI F64 rix:rx
  EPI F64 riy:ry
  EPI F64 riz:rz

  EPJ F64 rjx:rx
  EPJ F64 rjy:ry
  EPJ F64 rjz:rz
  EPJ F64 eps2:eps

  FORCE F64 fx:fx
  FORCE F64 fy:fy
  FORCE F64 fz:fz
  FORCE F64 p:p

  dx  = rix - rjx
  dy = riy - rjy
  dz  = riz - rjz
  r2  = dx * dx + dy * dy + dz * dz + eps2
  r2i = 1.0 / r2
  r6i = r2i * r2i * r2i
  f = (48.0 * r6i - 24.0) * r6i * r2i
  fx += f * dx
  fy += f * dy
  fz += f * dz
  p += 4.0 * r6i*(r6i - 1.0)

non-simd
\begin{tabular}{|l|r|r|} \hline
  N & Pyker & PIKG \\ \hline
  50000 & 40.736862 & 11.656278 \\
  25000 & 10.662050 & 3.521253 \\
  10000 & 0.985475 & 0.442775 \\
 \\ \hline
\end{tabular}

simd
\begin{tabular}{|l|r|r|} \hline
  N & Pyker & PIKG \\ \hline
  50000 & 3.702871  & 2.838773\\
  25000 & 0.838122 & 0.9904373 \\
  10000 & 0.134388 & 0.215270 \\

 \\ \hline
\end{tabular}
